Tidy data structure to support exploration and modeling of temporal-context data

### 2018-11-08 main.Rmd
new section on "Date structures"

@@

The "key" specification contributes to forming a tsibble alongside the index. The concept of "key" is introduced to identify units or subjects that are observed over time in a data table. In the wide format, each column holds a series of values, so that the column itself serves for the sake of identification. In the long format, all column names are melt to the corresponding "key" values. But the "key" is much more flexible than simply column names. Because it is not constrained to a single field, but can be comprised of multiple fields. The variables remain the same as it is, without additional manipulation to create the identifiers.

It is typically a priori known by users. The absence of key only occurs to a univariate case where the key is implicit. Multiple units must associate with an explicit "key" to allow for identification.

>>>>

# Data structures {#sec:str}

@@

The "key" specification contributes to creating a tsibble alongside the index. The concept of "key" is introduced to identify units or subjects that are observed over time in a data table. In the wide format, each column holds a series of values, so that the column itself serves for the sake of identification. In the long format, all column names are melt to the corresponding "key" values. But the "key" is much more flexible than simply column names. Because it is not constrained to a single field, but can be comprised of multiple fields. The identifying variables that the "key" is constituted of, remain the same as they are in the original table, with no additional manipulation.

Each tsibble must attach with a "key". It is normally a priori known by analysts. For example, Table \ref{tab:tb-sub} describes the number of tuberculosis cases for each gender across the countries every year. This data description suggests that columns `gender` and `country` have to be declared as the key. Lacking in either of two will be inadequate for the key and thus fail to construct a tsibble. The key is explicit when multiple units exist in the data. Key can be implicit when it finds a univariate series in the table, but it cannot be absent from a tsibble.
